% !TEX encoding = UTF-8
%======中文摘要内容格式:{中文摘要}{关键词}
\ZhAbstract{摘要应概括论文的主要信息，包括研究目的、研究方法、研究成果和最终结论等。注明论文关键词3—5个。硕士学位论文中文摘要一般为600-800字，博士学位论文中文摘要一般为1500字左右。中英文摘要内容要求一致。
	
	湖南师范大学创建于1938年，位于历史文化名城长沙，是国家“211工程”重点建设的大学，国家“双一流”建设高校，教育部与湖南省重点共建“双一流”建设高校，教育部普通高等学校本科教学工作水平评估优秀高校，湖南省“世界一流学科建设高校”。学校现有7个校区，占地2744余亩，建筑面积125余万平方米。主校区西偎麓山，东濒湘江，风光秀丽，是全国绿化“400佳”单位之一。

	学校设有24个学院，现招生本科专业81个，本科和研究生教育覆盖哲学、经济学、法学、教育学、文学、历史学、理学、工学、医学、管理学、艺术学等11大学科门类。学校拥有伦理学、英语语言文学、中国近现代史、发育生物学、理论物理、基础数学等6个国家重点学科，“语言与文化”学科群主建学科外国语言文学入选国家“世界一流”建设学科，教育学、数学、哲学、中国语言文学、生物学5个学科入选湖南省“国内一流建设学科”，法学、马克思主义理论、体育学、新闻传播学、物理学、化学、地理学、音乐与舞蹈学、美术学、政治学、心理学、中国史、生态学、理论经济学、统计学等15个学科入选湖南省“国内一流培育学科”;化学、临床医学2个学科进入ESI前1\%；拥有21个博士学位授权一级学科、教育博士专业学位授权类别、37个硕士学位授权一级学科和24种硕士专业学位授权类别，以及18个博士后科研流动站；拥有中国特色社会主义道德文化省部共建协同创新中心，拥有教育部人文社会科学重点研究基地湖南师范大学道德文化研究中心、国家体育总局体育社会科学重点研究中心；拥有中国语言文学、历史学国家文科基础学科人才培养和科学研究基地、国家生命科学与技术人才培养基地、全国大学生文化素质教育基地、教育部基础教育课程研究湖南师范大学中心、国家红色经典艺术教育示范基地、国家卓越法律人才教育培养基地、国家卓越中学教师培养计划实施院校、国家卓越医生教育培养计划项目试点高校、中华优秀传统文化传承基地（花鼓戏）、教育部体育美育浸润行动计划入选高校等16个国家级人才培养和科学研究基地（中心）；拥有省部共建淡水鱼类发育生物学国家重点实验室，石化新材料与资源精细利用、动物多肽药物创制2个国家地方联合工程实验室，2个省部共建国家重点实验室培育基地，4个省部共建教育部重点实验室，拥有多倍体鱼繁殖与育种技术教育部工程研究中心、农业部鲤鲫遗传育种中心；拥有1个省部共建“2011协同创新中心”、3个湖南省“2011协同创新中心”、拥有生物科学和中国语言文学2个湖南省基础学科拔尖学生培养基地。

	建校以来，学校已为国家输送毕业生50余万人，培养了一大批国际学生和港澳台学生，校友遍布海内外。在校学生4万余人，其中研究生1万余人，长短期国际学生近1200人，已形成多规格、多层次的办学格局。

	面向未来，湖南师范大学将始终秉承“仁、爱、精、勤”的校训精神，以立德树人为根本任务，立足湖南，服务全国，面向世界，坚定推进学校内涵发展、创新发展、特色发展、可持续发展、和谐发展，努力建设教师教育特色鲜明、国内一流、国际上有影响的高水平综合型大学。
}{湖南师范大学；211重点大学；双一流建设高校}
%======中文摘要内容格式:{英文摘要}{关键词}
\EnAbstract{Top-ranking  University HNU is a "211 project" university, ranking  60th among China's key 100 universities. In 2011, HNU was elected as one of  "Ten Famous Universities" by all the foreign students in China.

	First-class Living Condition The foreign  students' dormitory is constructed according to the Standard of three-star  hotel. Each room is with a pirate washing room and a balcony. In the room  there are a TV set, a fridge, a telephone, a water heater, internet service,  bookshelves, desks, soft simmons beds and etc.. Public laundry is in the  basement and public kitchens are located in each floor. The foreign students'  dormitory living fee is much cheaper than those in Beijing and Shanghai.

	Perfect Supporting Facilities About 50 meters  away from the foreign students' dormitory there are four banks and a Post  Office, where students can draw and deposit money and get Western Union  service. A super market and a students' dinning room is around 100 meters  away, where students can buy necessaries and get food. The university library  is 200 meters away, where is a good place for students to do individual  learning at the main teaching building where students have their classes is  about 5 minute walk and only 400 meters away.

	Excellent Chinese Teaching and Services A professional  college called International College of Chinese Language and Culture at HNU  is especially set up for foreign students to learn Chinese. In each class,  there are around 15 students and the college provides one-to-one Chinese  training. Specialists in the Office of International Exchange and Cooperation  offer admission services, airport pick-up, living and students' visa help.

	Welcome to Hunan Normal University!

	Founded in 1938, Hunan Normal University enjoys a history of 80 years. It is also one of the leading universities building under the national “211 project” and “Double First-Class Strategic Plan”.

	Hunan Normal University puts stress on fundamental and quality education, while placing equal stress on the cultivation of both application-oriented talents and research experts. Up to 2017, it has cultivated over 400,000 students. Hunan Normal University enjoys a high reputation in society for its excellent quality education. It now boasts 3 CFCRS (Chinese-foreign Cooperation in Running Schools) programs and 185 partner institutions in 45 countries and has co-established 3 Confucius Institutes in Russia, Korea and the U.S. respectively.

	Hunan Normal University embraces beautiful scenery and tranquil environment,  which offers you a pleasant atmosphere for studying Chinese and Chinese culture. We warmly welcome all overseas friends who are interested in Chinese culture to visit Hunan Normal University. We firmly believe that you will become excellent students who will be proficient in both Chinese and Chinese culture. Without doubt, your study here will provide you with life-long benefits.
}{HUNNU; 211 project; Double First-Class Strategic Plan}